The polynomial representation of the type $A_{n - 1}$ rational Cherednik algebra in characteristic $p \mid n$

### 2015-05-18 formalwriteup.tex
Convert vand to Lemma

\begin{proposition}\label{prop:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
\end{proposition}
\begin{proof} 
Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series. Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$. In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.  However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
\end{proof}

@@

Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Proposition~\ref{prop:vand} we see that the polynomials $b_i(z)$ are linearly independent.

>>>>

\begin{lemma}\label{lem:vand}Let $y_0, \ldots, y_{r - 1}$ be distinct elements of $k$.  Then the polynomials $b_i(z) = \prod_{j \neq i} (1 - y_j z)$ are linearly independent.
\end{lemma}
\begin{proof} 
Suppose that for some $\lambda_i \in k$ we have $\sum_i \lambda_ib_i(z)=0$.  Then $\left(\prod_j (1-y_jz)\right)\left(\sum_i \frac{\lambda_i}{1-y_iz}\right)$ must be $0$ in the ring of formal power series. Since the ring of power series is an integral domain, $\sum_i \frac{\lambda_i}{1-y_iz}=0$. In particular for $\ell=0,\dots,r-1$ we have $\sum_i \lambda_iy_i^\ell=0$.  However, the vectors $(1,y_i,\dots,y_i^{r-1})$ are linearly independent by the Vandermonde determinant, so $\lambda_i=0$ for all $i$, meaning that $b_i(z)$ are linearly independent.
\end{proof}

@@

Define $b_i(z)=\prod_{j \ne i} (1-y_jz)$ for $i=0,\dots,r-1$; then by Lemma~\ref{lem:vand} we see that the polynomials $b_i(z)$ are linearly independent.
